### 2023-12-21 manuscript.tex
. [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/77b476d159419ad0a5a90137e64696ffcef93452.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/77b476d159419ad0a5a90137e64696ffcef93452/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7286504801

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/77b476d159419ad0a5a90137e64696ffcef93452/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/77b476d159419ad0a5a90137e64696ffcef93452}{MMV-Lab/im2im-paper@77b476d}
on December 20, 2023.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/77b476d159419ad0a5a90137e64696ffcef93452/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/77b476d159419ad0a5a90137e64696ffcef93452}{MMV-Lab/im2im-paper@77b476d}
on December 21, 2023.
